### 2015-05-14 corral.tex
POR

\ADComment{Top-level questions on this section: do we make it clear how \corral identifies a race?  And do we make it clear enough that although in our experiments we consider accelerating race detection, we can more generally accelerate assertion checking?}

@@

\medskip\noindent\textbf{Sound Partial-Order Reduction }
%
By default, and assuming no race-freedom guarantees, \whoop instruments a \texttt{yield} statement (which denotes a potential nondeterministic context-switch) after each shared memory access of each entry point.\footnote{We acknowledge that in the presence of data races and relaxed memory, even considering all interleavings of shared memory accesses may be insufficient to find all bugs.} \ADComment{We should say here that lock/unlock operations also have yields.} \whoop then sends this instrumented program to \corral, which leverages sequentialization to explore all possible thread interleavings up to a pre-defined bound. Our approach to accelerating \corral is simple and yet effective: we simplify the sequentialization that \corral performs by instrumenting \texttt{yield} statements only at shared memory accesses that \whoop reported as potentially racy. This effectively acts as a partial-order reduction that can significantly reduce the number of interleavings that \corral needs to explore, and thus increase performance and scalability.

We now argue that our partial-order reduction is sound: it does not cause \corral to miss any additional bugs.
\ADComment{Let's go over this together.}
Let \corral run an $n$ amount of entry point pairs with yields after all \emph{visible} operations (synchronization points and shared memory accesses). Let this configuration be known as $C$. Each entry point pair is running in a separate \corral process. \corral will miss all bugs that are triggered by more than 3 threads running concurrently and all bugs that are triggered by investigating a larger than $r$ recursion bound and larger than $k$ context-switch bound. Let \corral then run the same $n$ amount of pairs, but this time \whoop removes the \texttt{yield} statements after all non-racy shared memory accesses. Let this configuration be known as $W+C$. Because these shared memory accesses cannot race, performing a \texttt{yield} will not introduce any new program behaviors. Thus, \corral will find the same bugs using the configuration $W+C$, as using the configuration $C$.

>>>>

\ADComment{Suggestions: discuss race instrumentation for Corral immediately after explaining how corral works.  Don't say ``we regard races as bugs''.  After POR part, emphasise that this idea can be used to accelerate Corral for arbitrary bug-finding in concurrent programs.  Then make it clear that in the remainder of the paper we regard races as bugs and use corral solely to look for races.}

@@

\medskip\noindent\textbf{Sound Partial-Order Reduction }
%
By default, and assuming no race-freedom guarantees, \whoop instruments a \texttt{yield} statement (which denotes a potential nondeterministic context-switch) after each shared memory access of each entry point, and after every lock and unlock operation.\footnote{We acknowledge that in the presence of data races and relaxed memory, even considering all interleavings of shared memory accesses may be insufficient to find all bugs.} \whoop then sends this instrumented program to \corral, which leverages sequentialization to explore all possible thread interleavings up to a pre-defined bound. Our approach to accelerating \corral is simple and yet effective: if, thanks to \whoop's analysis, we know that a given statement that accesses shared memory cannot be involved in a data race, we do not instrument a \texttt{yield} after this statement.  This is a form of \emph{partial order reduction}~\cite{DBLP:books/sp/Godefroid96}, and reduces the number of context switches that \corral must consider in a \emph{sound} manner: there is no impact on the bugs that will be detected.  This is because each access for which a \texttt{yield} is suppressed is guaranteed to be protected by some lock (a consequence of lockset analysis).  If the access is a write, its effects are not visible by the other entry point until the lock is released.  If the access is a read, the value of the shared location cannot change until the lock is released.  The fact that a \texttt{yield} is placed after each unlock operation suffices to take account of communication between entry points via the shared memory location.
